---
title: "Linear Regression: How it works, in 30 minutes"
date: '`r Sys.Date()`'
output: github_document
---

<div>
  <a href="https://creativecommons.org/licenses/by-nc-sa/4.0/legalcode"><img src="https://img.shields.io/badge/license-CC BY--NC--SA 4.0-green?style=flat-square&logo=creative-commons"></a>
  <a href="https://mit-license.org/"><img src="https://img.shields.io/badge/license-MIT-green?style=flat-square"></a>
</div>

```{r knitr-setup, echo = FALSE}
knitr::opts_chunk$set(echo=FALSE)

options(knitr.kable.NA = "-")
```

```{r packages, message = FALSE}
library(magrittr)
library(tibble)
library(dplyr)
library(tidyr)
library(purrr)
```
This slide deck covers the fundamentals of linear regression from an 
application/purpose perspective. 

It's not intended to be a resource on how to build a model with code. 

Focus is on the underlying ML principles and how they relate to using linear 
regression in the real world.

Below is a basic lesson plan oriented around the [Level 4 Data Analyst](https://www.instituteforapprenticeships.org/apprenticeship-standards/data-analyst/)
apprenticeship standards.

## Lesson Plan

**Intended Audience:** Level 4. 

**Assumptions:**

  - No prior knowledge of linear regression is assumed
  - Familiarity with the benefit of problem solving with machine learning may 
    already be known, but is not assumed
  - Familiarity with scatter plots, and the concept of correlation is assumed

### Data Analyst Level 4 Standards (v1.1)

Core standards supported by learning in this session:

```{r ksb-plan-data}
# Read-in data as tibbles
ksbs <- yaml::read_yaml("ksb.yml") %>% 
  map(.f = ~map_dfr(., .f = as_tibble))

# Join and format data
ksbs_table <- left_join(ksbs$this_session, ksbs$sets, by = "set") %>% 
  left_join(ksbs$ams, by = "am") %>% 
  select(-set, -am) %>% 
  unite(col = ksb, ksb, desc, sep = ": ") %>% 
  pivot_wider(names_from = am_name, values_from = ksb) %>% 
  relocate(matches("AM1"), .after = 1)
```

```{r kbl-ksb-list}
# KSB plan as kable
knitr::kable(
  ksbs_table,
  col.names = c("Group", colnames(ksbs_table)[2:3]),
  row.names = F
)
```

Note that this list is not exhaustive, other standards will be addressed by
applying linear regression in real-world contexts (e.g. standards on 
data acquisition, cleaning, exploratory data analysis, visualization etc).

### Approximate Timing

- **5mins**: 
    - intro; scope and purpose
    - **ask for learner input**: machine learning (purpose and approach) 
      knowledge. 
    - Illustrate machine learning concept with ingredients/cookies analogy if
      needed
- **5-15mins**: ingredients/calories business scenario
    - highlight this is a regression problem because it involves continuous data 
      types
    - scatter plot, correlation
    - add a linear model
    - intercept / gradient
    - combine together
- **5-10mins**: (possibly a stretch topic)
    - **ask for learner input**: what makes a model good? how can we quantify 
      success?
    - variance explained
    - residuals
    
